The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-05 paper/ms.tex
Slightly update Ji hist plots

\subsection{The Local Midplane} \label{ssec:local_midplane}
Using the two sets of simulations, we determine the local midplane that an
observer might measure if they were situated in each of these galaxies as a
function of azimuth at the solar circle. Starting from the coordinate system
described in the previous section, which is approximately aligned so that the
$z$-coordinate is perpendicular to the disk plane, we place our imaginary
observer at $z=0$ and a galactocentric cylindrical radius of $8.2\,\kpc$ and vary the azimuth
between $0<\phi<2\pi$.\footnote{The immortal observer also has warp drive, allowing them to travel around the galaxy much more quickly than its dynamical timescale (warp factor $\sim0.25$). Using warp drive allows them to sidestep time dilation effects.} At
each value of $\phi$ we then compute the median $z$ for stars within a
cylinder of radius $0.5\,\kpc$ and height $1\,\kpc$ perpendicular to the
fiducial disk. We then re-define the new midplane of the cylinder to be the
median $z$, re-select stars, and iterate until the median $z$ value converges.
We find that only $10$ iterations of this procedure are necessary for
convergence. The resulting median $z$ is taken to be what our observer would
measure as the local Galactic midplane at each $\phi$.

>>>>

\subsection{The Local Midplane} \label{ssec:local_midplane}
Using the two sets of simulations, we determine the local midplane that an
observer might measure if they were situated in each of these galaxies as a
function of azimuth at the solar circle. Starting from the coordinate system
described in the previous section, which is approximately aligned so that the
$z$-coordinate is perpendicular to the disk plane, we place our imaginary
observer at $z=0$ and a galactocentric cylindrical radius of $8.2\,\kpc$ and vary the azimuth
between $0<\phi<2\pi$.\footnote{The immortal observer also has warp drive, allowing them to travel around the galaxy much more quickly than its dynamical timescale (warp factor $\sim0.25$). Using warp drive allows them to circumvent time dilation effects.} At
each value of $\phi$ we then compute the median $z$ for stars within a
cylinder of radius $0.5\,\kpc$ and height $1\,\kpc$ perpendicular to the
fiducial disk. We then re-define the new midplane of the cylinder to be the
median $z$, re-select stars, and iterate until the median $z$ value converges.
We find that only $10$ iterations of this procedure are necessary for
convergence. The resulting median $z$ is taken to be what our observer would
measure as the local Galactic midplane at each $\phi$.
